---
title: "CTS"
author: "John Lyons"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(dygraphs)
library(dplyr)
library(quantmod)
library(xts)
library(plotly)
library(flexdashboard)
library(readxl)
library(gplots)
library(RColorBrewer)
library(reshape2)
source('~/Documents/Personal/DataScience/R/JL CTS scripts/fnCumRet.R')
JSEdat <- read.csv("/Users/johnlyons/Documents/Personal/DataScience/R/JSEdat.csv", header = TRUE)
JSEdat <- JSEdat[,-1]
JSEdat$Date <- as.Date(JSEdat$Date)
JSEdat$Name <- gsub("-","_",JSEdat$Name)
JSEdat$Name <- gsub("_\\$","",JSEdat$Name)
alldata2 <- unique(subset(JSEdat,JSEdat$Date >= Sys.Date()-20))


Trades <- read_excel("/Users/johnlyons/Dropbox/CTS/Trades.xlsx",col_names = TRUE,na = "")
Trades <- as.data.frame(Trades)
Trades$Purchase <- as.Date(Trades$Purchase)
Trades$`Exit Dt` <- as.Date(Trades$`Exit Dt`)
mylst <- subset(Trades,is.na(Trades$Exit)) 
instLive <- as.character(sort(mylst[,1]))
Metals <- c("BRENT","COPPER","ZINC","IRONORE","NICKEL","PALLAD","GOLD_R","GOLD_PM","PLAT","SILV","SILV_R")
Metals1 <- c("BRENT","COPPER","ZINC","NICKEL","PALLAD","GOLD_R","GOLD_PM","PLAT","SILV","SILV_R")
KeyIndixes <- c("JSE_OILG","JSE_AUTM","JSE_CONS","JSE_INDI","JSE_PLAT","JH_ALSI40","JSE_TECH","JSE_FINI","JSE_BANK","JSE_PHAR","JSE_HEAL","GOLD_R","JSE_GOLD","JSE_COAL","JSE_RESI","JSE_INDM","JSE_METL","USALB","SP500","NIKKEI")
indi <- c("JSE_INDI","NETCARE","LIFEHC","STEINHOFF","PICKNPAY","WOOLIES","TRUWTHS","RICHEMONT","MTN","MEDCLIN","CLICKS","VODACOM","BIDVEST","TFG","MRPRICE","IMPERIAL","SPAR","SHOPRIT","REMGRO","BIDCORP","ASPEN","TIGBRANDS","BATS","NASPERSN")
Cons <- c("JSE_CONS","ADVTECH","BIDCORP","CHOPPIES","CITYLDG","CLICKS","CURRO","CASHBIL","FAMBRANDS","HOLDSPORT","ITLTILE",
          "MRPRICE","MASSMART","NASPERSN","PICKNPAY","SHOPRIT","SPAR","SUNINT","TFG","TRUWTHS","WOOLIES")
Curr <- c("C_EURZAR","C_GBPZAR","C_USDZAR","C_NZDZAR","C_ZARJPY","C_USDAUD","C_USDCAD","C_USDCHF","C_USDGBP","C_USDEUR","C_USDJPY","C_USDEUR","C_USDCNY","C_BTCUSD","C_BTCZAR")
Watchlist <- c("ALTRON","ARGENT","ARM","EXXARO","EOH","HARMONY","KUMBAIO","MONTAUK","VODACOM","MERAFE","METAIR","MRHLD","SASOL","STEFSTOCK","STELLAR","MASSMART","ASTRAL","SAPPI","BLUETEL","IMPERIAL","WOOLIES","SANLAM","SHOPRIT","DRDGOLD")

### Build ea of the xts datasets ###
mylist <- c(instLive,KeyIndixes,Metals,indi,Cons,Curr,Watchlist)

for(i in mylist) {
        y <- subset(JSEdat,JSEdat$Name == i)
        z <- xts(y[,3:7],order.by = y[,2])        # convert to xts
        zw <- to.period(z,"weeks")
        #z <- tail(z,90)                         # last 90 days
        assign(i,z)                              #Daily data
        assign(paste(i,"W",sep=""),zw)           #Weekly data
}

```

Live {data-icon="fa-area-chart"}
====================================================================

Inputs {.sidebar data-width=130}
--------------------------------------

```{r}
dateInput(inputId = "dtChoice1",
           label = "Choose a start date ",
           value = "2018-02-01")

selectInput(inputId = "indicator",
             label = "Select instrument", 
             selectize = FALSE,
             choices = sort(instLive))


```

Column 
-------------------------------------
    
### Daily Chart

```{r}
data <- reactive({
        eval(parse(text = input$indicator)) 
})
        
renderPlot({    
    chartSeries(data(), 
                subset = paste(Sys.Date()-200,"::",sep=""),
                #subset = paste(input$dtChoice1,"::",sep=""),
                name = input$indicator,theme = "white", up.col = "blue",dn.col = "red",TA="addOBV();addSMA(n=24);addMACD();addVo();addBBands()")
  })
```

Column {.tabset}
-------------------------------------
    
### Weekly Chart

```{r}
data <- reactive({
        eval(parse(text = input$indicator)) 
})
        
renderPlot({    
    chartSeries(to.weekly(data()), 
                subset = ("2016-01::"),
                #subset = paste(input$dtChoice1,"::",sep=""),
                name = input$indicator,theme = "white", up.col = "blue",
                dn.col = "red",TA="addOBV();addSMA(n=24);addMACD();addVo();addBBands()")
  })
```



### Weekly DyGraph

```{r}
dataW1 <- reactive({
        eval(parse(text = paste(input$indicator,"W",sep="")))
})

Entry <- reactive({
        (filter(mylst,Instrm == input$indicator)  %>% select(EntryPrice))[1,1]       # Get entry and stop loss lev
})

StopL <- reactive({
        (filter(mylst,Instrm == input$indicator)  %>% select(StopLoss))[1,1]       # Get entry and stop loss lev
})

renderDygraph({
    dataW1()[,2:4][paste(input$dtChoice1,"::",sep="")] %>%        
    dygraph(dataW1(),main = as.character(input$indicator)) %>%
    dySeries(c("z.Low","z.Close","z.High")) %>%
    dyLimit(Entry(), color = "green") %>%
    dyLimit(StopL(), color = "red")                
  })
```

KeyIndexes {data-icon="fa-area-chart"}
====================================================================
Inputs {.sidebar data-width=200}
--------------------------------------

```{r}

dateInput(inputId = "dtChoice2",
           label = "Choose a start date ",
           value = "2018-02-01")
selectInput(inputId = "index",
             label = "Select instrument", 
             selectize = FALSE,
             choices = sort(KeyIndixes))
```


Column {data-width=400}
-------------------------------------
### Weekly 

```{r}
dataInd <- reactive({
        eval(parse(text = paste(input$index,"W",sep="")))
})

renderDygraph({
    dataInd()[,2:4][paste(input$dtChoice2,"::",sep="")] %>%        
    dygraph(dataInd(),main = as.character(input$index)) %>%
    dySeries(c("z.Low","z.Close","z.High")) 
  })
```


Column {.tabset,data-width=300}
-------------------------------------

### CumulativeReturns

```{r}

fnCumRet("2018-0-04",KeyIndixes)
renderPlot({   
    
    plot(x = zoo.dp, ylab = "Cumulative Return %age", main = "KeyIndexes", col = tsRainbow, screens = 1,lwd = 2.5)
    grid(NULL,NULL)
    abline(h=0)
    #legend("topleft",legend = KeyIndixes,inset=0.01,cex = 0.9,lty=c(1),lwd=c(3),bg="grey96",col = tsRainbow ) 
  })

```

Column {data-width=200}
-------------------------------------
    
### TableOfReturns

```{r}

renderTable({   
    tor
  })
```

Commodities {data-icon="fa-area-chart"}
====================================================================
Inputs {.sidebar data-width=200}
--------------------------------------

```{r}

dateInput(inputId = "dtChoice3",
           label = "Choose a start date ",
           value = "2018-02-01")
selectInput(inputId = "metals",
             label = "Select instrument", 
             selectize = FALSE,
             choices = sort(Metals))

```


Column {data-width=400}
-------------------------------------
### Weekly 

```{r}
dataMet <- reactive({
        eval(parse(text = paste(input$metals,"W",sep="")))
})

renderDygraph({
    dataMet()[,2:4][paste(input$dtChoice3,"::",sep="")] %>%        
    dygraph(dataMet(),main = as.character(input$metals)) %>%
    dySeries(c("z.Low","z.Close","z.High")) 
  })
```

Column {.tabset}
-------------------------------------
### ChartSeries Comparative - Commodities

```{r}

for(i in Metals1) {
        y <- subset(alldata2,alldata2$Name == i)
        y <- y[,c("Date","Close")]
        y <- aggregate(Close ~ Date, y, mean)   # get rid of dups and multiple entries
        zz <- xts(y[,2],order.by = y[,1])        # convert to xts
        assign(i,zz)
        }
mm <- sapply(Metals1,as.name)                     # assign string from mylst names to xts sets

myxts <- do.call(merge,sapply(Metals1,as.name))   # build single xts frame of instr closing prices
day1 <- as.numeric(myxts[1,])                   #get closing price of first record
dpMet <- head(myxts,0)                             # price on day1 of set
for(i in 1:ncol(myxts)) {                       # build xts frame of instr and %age moves
       pcage<- ((myxts[,i] - day1[i])  / day1[i] )*100         
        dpMet  <- cbind(dpMet,pcage)
        }

zoo.dpMet <- as.zoo(dpMet)                    #convert to zoo to keep column names
# Set a color scheme:
tsRainbow <- rainbow(ncol(zoo.dpMet))
templst <- as.data.frame(tail(dpMet,1))
templst <- melt(templst)                        #cast long
templst$value <- round(templst$value,2)
torMet <- templst[order(templst[,2],decreasing = TRUE),]

renderPlot({   
    
    plot(x = zoo.dpMet, ylab = "Cumulative Return %age", main = "Commodities", col = tsRainbow, screens = 1,lwd = 2.5)
    grid(NULL,NULL)
    abline(h=0)
    legend("bottomleft",legend = Metals1,inset=0.01,cex = 0.9,lty=c(1),lwd=c(3),bg="grey96",col = tsRainbow ) 
  })

```

    
### ChartSeries

```{r}
dataMetal <- reactive({
        eval(parse(text = input$metals)) 
})
        
renderPlot({    
    chartSeries(dataMetal(), subset = paste(input$dtChoice2,"::",sep=""),name = input$metals,theme = "white", up.col = "blue",dn.col = "red",TA="addSMA(n=24);addBBands()")
        

  })
```

Column {data-width=200}
-------------------------------------
    
### TableOfReturns

```{r}

renderTable({   
    torMet
  })
```

Indi {data-icon="fa-area-chart"}
====================================================================
Inputs {.sidebar data-width=200}
--------------------------------------

```{r}

dateInput(inputId = "dtChoice4",
           label = "Choose a start date ",
           value = "2018-02-01")
selectInput(inputId = "indi",
             label = "Select instrument", 
             selectize = FALSE,
             choices = sort(indi))

```


Column {data-width=500}
-------------------------------------
### Weekly 

```{r}
dataI <- reactive({
        eval(parse(text = paste(input$indi,"W",sep="")))
})

renderDygraph({
    dataI()[,2:4][paste(input$dtChoice4,"::",sep="")] %>%        
    dygraph(dataI(),main = as.character(input$indi)) %>%
    dySeries(c("z.Low","z.Close","z.High")) 
  })
```

Column {data-width=500}
-------------------------------------
    
### ChartSeries

```{r}
dataIndi <- reactive({
        eval(parse(text = input$indi)) 
})
        
renderPlot({    
    chartSeries(dataIndi(), subset = paste(input$dtChoice4,"::",sep=""),name = input$indi,theme = "white", up.col = "blue",dn.col = "red",
TA="addOBV();addSMA(n=24);addMACD();addVo();addBBands()")                
             
  })
```

Cons {data-icon="fa-area-chart"}
====================================================================
Inputs {.sidebar data-width=200}
--------------------------------------

```{r}

dateInput(inputId = "dtChoice5",
           label = "Choose a start date ",
           value = "2018-02-01")
selectInput(inputId = "cons",
             label = "Select instrument", 
             selectize = FALSE,
             choices = sort(Cons))

```


Column {data-width=500}
-------------------------------------
### Weekly 

```{r}
dataC <- reactive({
        eval(parse(text = paste(input$cons,"W",sep="")))
})

renderDygraph({
    dataC()[,2:4][paste(input$dtChoice5,"::",sep="")] %>%        
    dygraph(dataC(),main = as.character(input$cons)) %>%
    dySeries(c("z.Low","z.Close","z.High")) 
  })
```

Column {data-width=500}
-------------------------------------
    
### ChartSeries

```{r}
dataCons <- reactive({
        eval(parse(text = input$cons)) 
})
        
renderPlot({    
    chartSeries(dataCons(), subset = paste(input$dtChoice5,"::",sep=""),name = input$cons,theme = "white", up.col = "blue",dn.col = "red",
TA="addOBV();addSMA(n=24);addMACD();addVo();addBBands()")                
             
  })
```

Curr {data-icon="fa-area-chart"}
====================================================================
Inputs {.sidebar data-width=200}
--------------------------------------

```{r}

dateInput(inputId = "dtChoice6",
           label = "Choose a start date ",
           value = "2018-02-01")
selectInput(inputId = "curr",
             label = "Select instrument", 
             selectize = FALSE,
             choices = sort(Curr))

```


Column {data-width=500}
-------------------------------------
### Weekly 

```{r}
dataCr <- reactive({
        eval(parse(text = paste(input$curr,"W",sep="")))
})

renderDygraph({
    dataCr()[,2:4][paste(input$dtChoice6,"::",sep="")] %>%        
    dygraph(dataCr(),main = as.character(input$curr)) %>%
    dySeries(c("z.Low","z.Close","z.High")) 
  })
```

Column {data-width=500}
-------------------------------------
    
### ChartSeries

```{r}
dataCurr <- reactive({
        eval(parse(text = input$curr)) 
})
        
renderPlot({    
    chartSeries(dataCurr(), subset = paste(input$dtChoice6,"::",sep=""),name = input$curr,theme = "white", up.col = "blue",dn.col = "red",TA="addSMA(n=24);addBBands()")                
             
  })
```

Watchlist {data-icon="fa-area-chart"}
====================================================================
Inputs {.sidebar data-width=200}
--------------------------------------

```{r}

dateInput(inputId = "dtChoice7",
           label = "Choose a start date ",
           value = "2018-02-01")
selectInput(inputId = "wl",
             label = "Select instrument", 
             selectize = FALSE,
             choices = sort(Watchlist))

```

Column {data-width=500}
-------------------------------------
### Weekly 

```{r}
dataWl <- reactive({
        eval(parse(text = paste(input$wl,"W",sep="")))
})

renderDygraph({
    dataWl()[,2:4][paste(input$dtChoice7,"::",sep="")] %>%        
    dygraph(dataWl(),main = as.character(input$wl)) %>%
    dySeries(c("z.Low","z.Close","z.High")) 
  })
```

Column {data-width=500}
-------------------------------------
    
### ChartSeries

```{r}
dataWal <- reactive({
        eval(parse(text = input$wl)) 
})
        
renderPlot({    
    chartSeries(dataWal(), subset = paste(input$dtChoice7,"::",sep=""),name = input$wl,theme = "white", up.col = "blue",dn.col = "red",TA="addOBV();addSMA(n=24);addMACD();addVo();addBBands()")             
             
  })
```


Heatmap {data-icon="fa-table"}
====================================================================

### Explore the data as selected

```{r} 
 #data <- reactive({
 #       eval(parse(text = input$indicator))
#})
#render({
#        filter(JSEdat,JSEdat$Name == input$indicator)   
#        options = list(pageLength = 50)}) 

```


-- applying more changes